Molecular Gas Kinematics of the Strongly-lensed Quasar Host Galaxy RXS J1131$-$1231

### 2016-11-15 WRITEUP/response.md

We thank the referee for providing constructive and thoughtful
comments to improve the manuscript. We have addressed all the concerns
raised by the referee and details can be found in the revised version of the manuscript -- please see attached. A brief description on how we incorporated the referee's suggestions can be found below.

1a) We have changed the title to "Molecular gas kinematics of the strongly lensed quasar host galaxy RXS\,J1131-1231".
We agree that we study more than just the CO gas of the science target in this paper; however, a large fraction of the paper is based on our new CO data and the analysis (incl. lens modeling). Therefore, we think that the title is suitable for the paper.

The literature/archival data of the continuum would not be as meaningful without our CO data, e.g. their emission does not convey inforamtion about the kinematics, spatial distribution, and does not give a broader picture regarding the f_gas evolution, which is one of the main conclusions found in this study.

1b) We took this suggestion. To minimize potential confusion, we have changed "dynamically resolved" to "kinematically resolved".

1c) We took this suggestion and have updated our redshift (and re-plotted the figure) based on the results from fitting a double-Gaussian to the de-lensed intrinsic line profile of our target (Fig. 5).

1d) We took this suggestion and have changed "dynamical information" to "kinematic information", "reconstruct the intrinsic gas dynamics" to "reconstruct the intrinsic line profile and source-plane velocity structure".

We have rephrased the 2nd paragraph of Sec 4.1.2 to clarify what we meant.

2a) We took this suggestion and have corrected nu_LO --> nu_obs.

2b) We took this suggestion and re-fitted a doubled Gaussian to the de-lensed profile (Fig. 5) and updated the redshift and replotted all the relavent figures (and updated their captions correspondingly), updated column 1 in Table 3, the labeling in Fig 7, refitted the model shown in Fig. 9 and updated parameters in Sec 4.3 correspondingly, SED fitting, etc.

3) 
We found a bug in generating the map used for previous line-integrated flux extraction. In the resubmitted version, we have updated the intensity reported for CO(2-1) by summing the fluxes in the relavent channels, which is in agreement with the double-Gaussian fit to the spatially extracted spectrum (Fig. 1). Since our lensing-corrected M_gas for both RXJ1131 and the companion are derived from the flux in each channel, this doesn't change our conclusion.

We tried adding the companion's spectrum to plot (Fig. 5) but found the figure to be over-crowded/too busy, as there are already showing various things with different various linestyles, colors. This main message for this plot is to show that we find that the intrinsic profile of the main galaxy is symmetric, which is informative about the kinematics of this galaxy. On the other hand, the useful info for the companion from the de-lensed spectrum is the gas mass, which we report in the text (and in the table, as suggested by the referee).

Source size: We fitted a single Guassian in uv-plane to support the reported CO size based on image plane fitting, of which the convolved size is 6.6+/-0.5 x 4.5+/-0.3. We additionally report the source sizes by fitting two Gaussians to provide further evidence that the CO(2-1) emission is resolved. We have updated Section 3.1 to clarify the discussion.

CO physical size:
The rough estimate of de-magnified CO diameter provided in the referee report is flawed since it assumes the magnification factor to be constant along the arc. The fact that 
1) the lensed emission is not uniformly stretched along the arc (and contains complex structures within the arc)
2) CO is immune to dust extinction, therefore likely to be more extended than the optical emission, as supported by our deconvolved CO source size and in Fig. 7 (where the blue wing centroid is further out than the lensed arc), and from the results of our lens models 
indicates the CO source size is unlikely to be R ≤ 3.5 kpc.

The reported R_CO = 6 kpc is obtained based on the most extended kinematic component is consistent, see Sec 4.3.

4) While the most extreme peak to peak noise is ~100 mJy/beam, the noise varies across channels, and therefore, on average, sigma is lower across all channels. Thus, the uncertainty is more representative using those obtained from the integrated map.

To demonstrate that our S/N are real regardless of the fainter blue wing, we have independently obtained SNR map to confirm our results, where the peak flux in the red peak is 11.46+/-1.95 Jy/B and the blue peak is 5.13 +/- 1.45 Jy/B. 
I think what was confusing was the reported I_CO(3-2)=35.7+/-21.3Jy km/s, for which I missed a sqrt, and it should have been 35.7+/-6.91 Jy km/s, which has been corrected.

Since both CO lines are observed towards the same source, using prior knowledge about the blue wing from the CO(2-1) data to inform about the CO(3-2) emission is reasonable.

While the additioanl figure in I_CO is not significant, we keep this 
to enable reproducible results and to minimize cumulative errors (e.g. when compiled for a larger number of samples). We only report significant figures when reporting the physical parameters.

5) 
We updated the 2mm flux in Table 1. We updated the flux uncertainty to include those from the uv-fitting process.

The peak emission in the residual map is 0.39 +/- 0.08 mJy. While the uncertainty associated with the flux measurement of the background source needs to propagate the errors from subtracting the fitted model flux, the significance of the emission in the residual doesn't not. It simply is Data-Model, which is > 4 sigma than the noise. This together with the co-spatial emission supports that flux contributiion from the background source to the total integrated 2mm continuum.

The term "deblending" is a broadly used in photometry, and it is clear that it refers to the flux subtraction within the same paragraph. We therefore make no changes to the wording.

6) While the large uncertainty on the flux density of the background source at 2mm results in a spectral index with a large uncertainty, this nevertheless is a constraint on the radio-mm spectral slope: our value of -0.345 is flatter than the typical spectral index for pure synchrotron emission, suggesting that the 2mm has a non-negligible contribution from the underlying free-free emission. We have also added an additional statement stating that if there is a non-negligible contribution from the background source contributing to the peak flux, then the derived spectral index for the background source would be shallower, and therefore increasing the fraction of free-free emission over synchrotron at 2mm. This would also explain the atypical flat spectrum found for the foreground galaxy.

The flatter than pure synchrotron spectral slope found for the background source indicates that the 2mm continuum emission is not dominated by synchrotron. Assuming a synchrotron index of alpha = 0.7, we find 0.12 mJy at 2mm for the background source. To account for it, we have updated our SED fitting and the resulting parameters throughout the paper using S = 0.27 mJy at 2mm.

We note that 0.27 mJy is consistent with our previous flux measurement used for SED fitting (0.39+/-0.23 mJy) within the unceratinties, where this uncertainty included in the fit included those from absolute flux calibration. Therefore changes to the physical parameters are only at most a few percent,  we have updated the numbers but this does not alter the conclusions of this paper.

7) We adopted the suggestions.

8) We adopted the suggestions and have added additional tables summarizing the observed CO line properties and the derived physical parameters.

9) It is of standard practice to report flux measurmenets from interferometric observations excluding those from the absolute flux calibration. To address the referee's concern, we have added a remark in Section 3.3, table 1, and Sec 4.5 para 1 to avoid possible confusion for readers.

We have fixed the number of decimals in spectral indices in Sec 3.3.

10) We have replotted the figure with different contour intervals with thinner lines and added a sentence in the caption to improve clarify of Fig 4.

11) We have corrected "blueshifted" to "redshifted", udpated the velocity offset from 780 km/s to 715 km/s using z = 0.65406.

12) 
a)

We have removed the statement regarding "AGN dynamically offset".

# While the AGN may not be dynamically offset, given the possible scenario dirivng the BLR velocity offset, as pointed out by the referee, our CO measurement confirms that an offset between BLR and the systemic redshift, which is not known/constrained previously. We updated this section. The dynamical timescale of a recoiling black hole...

b & c) The details of the model (e.g. how we reconstruct the likelihood functions) are already referenced in other papers. We did not discuss any of that in this paper.

However, description of our MCMC sampling has been retained given that conveying the priors and stating how we ensure convergence is necessary for reproducible results and are crucial information for readers to decide on how trust-worthy our inference are from a statistical viewpoint. Explicitly stating the priors is important to demonstrate that our choice are reasonable and physically motivated since they could affect the marginal posteriors strongly and thus the inferred physical parameters.

13) We updated f_gas and f_mol using M_gas and M_dyn of both RXJ1131+companion , i.e., as a merger system.

For other comments, please refer to our response to point 11 and 12 (since 
they are repeated here).

14) 
Indeed, the plot on the left is to demonstrate that despite the observed 1st moment map is distorted due to a combination of differential lensing (in which the red velocity are more heavily weighed) and beam smearing effect, our dynamical lens modeling approach, which finds the best-fit models by taking into account the beam convolution indirectly, has enabled us to reconstruct the source-plane kienamtic components, as shown atop of the observed map. The reconstructed information displays a clear velocity gradient. Taken together with previous results from literature and the intrinsically symmetric line profile, we proceed the next section with dynamical modeling.

To address the referee's concern, we have added in a few lines in the caption to clarify what is being shown in the left panel.

PV: 
As discussed in Sec 4.1.1, we have detailed the evidence and reasons for which we interpret RXJ1131 as a disk galaxy. Under this assumption, the markers on the right plot are based on extracting along a fitted major axis of a disk (see first paragraphy of Sec 4.3).

To address the referee's concern and to improve clarify, we have re-iterate in the beginning of the first paragraph of Sec 4.3 that we interpret RXJ1131 as disk galaxy.

Size:
As explained in para. 3 of sec 4.3, we use the maximum observed velocity (i.e.  corresponding to the redmost channel along the disk major axis) at 6+/-3kpc as a proxy to the rotation velocity. Thus the quoted CO disk radius corresponds to the extent of this velocity component, as measured from the line center.

Clumps:
With the evidence and reasons listed in the begining of Sec 4.3, the reconstructed source-plane distribution is unlikely to be just two kinematically-ordered clumps rather than a single rotating disk.

### 2016-11-15 WRITEUP/ms.tex
taking into account everything in referee report, need to decide on BH recoil

\citestyle{aa}
\shorttitle{Molecular Gas Dynamics in the Strongly-lensed Quasar Host Galaxy RXJ1131$-$1231}
\shortauthors{Leung, Riechers \& Pavesi}

@@

\title{Molecular Gas Dynamics of the Strongly-lensed Quasar Host Galaxy RXS J1131$-$1231}
\author{T. K. Daisy Leung, Dominik A. Riechers, and Riccardo Pavesi}
\affil{Department of Astronomy, Space Sciences Building, Cornell University,
Ithaca, NY 14853, USA; \myemail}

@@

\begin{abstract}
We report observations of \bco and \cco line emission towards
the quadruply-lensed quasar
RXS\,J1131$-$1231 at $z$\,=\,0.654 obtained using the
\pdbi (PdBI) and the \carma (CARMA).
Our lens modeling shows that the asymmetry in the double-horned \bco line profile
is mainly a result of differential lensing, where
the magnification factor varies from $\sim$3 to $\sim$9 across
different kinematic components.
The intrinsically symmetric line profile with a conspicuous source-plane velocity
gradient suggests that
the host galaxy is an extended rotating disk, with a CO size of $R_{\rm CO}$$\sim$6\,kpc and
a dynamical mass of $M_{\rm dyn}$\ssim8\E{10}\,\Msun.
In addition, we find a secondary CO-emitting source near RXS\,J1131$-$1231 whose location is
consistent with the optically-faint companion reported in previous studies.
The lensing-corrected molecular gas masses are $M_{\rm gas}$\ssim1.4\E{10}\,\Msun
and \ssim2\E{9}\,\Msun for RXS\,J1131$-$1231 and the companion, respectively.
The gas mass fraction of $\sim$19\% inferred for RXS\,J1131$-$1231 is consistent with the trend of decreasing molecular gas fraction since $z$\ssim2 reported in recent studies.
We find lensing-corrected stellar and dust masses, an IR luminosity, and a
star formation rate of
$M_{*}$\ssim3\E{10}\,\Msun, $M_{\rm dust}$\ssim4\E{8}\,\Msun, $L_{\rm IR}$\ssim1.5\E{12}\,\Lsun,  and SFR$_{\rm FIR}$\ssim120\,\sfrU for RXS\,J1131$-$1231.
The source-plane morphologies of its gas and stellar populations
indicate that the star-formation activity may be as extended as the molecular gas reservoir.
We find a $M_{\rm BH}$$/$$M_{\rm bulge}$ ratio of $>$0.27\petm{11}{8}\% which is higher
than the 
local value, suggesting that the bulk of the black hole mass of RXSJ1131-1231 is largely in place while its stellar bulge is still assembling.
\end{abstract}

@@

%--------------------------------------------------------------------------
%                          Observations details
%--------------------------------------------------------------------------
\section{Observations} \label{sec:obs}
\subsection{PdBI \bco}
Observations of the \bco rotational line
($\nu_{\rm rest}$\,=\,$230.53800$ GHz)
at the $\nu_{\rm LO}$\eq139.256\,GHz
% redshifted to $\nu_{\rm obs}$\eq139.40739\,GHz
were carried out using IRAM \pdbi (PdBI; Program ID: S14BX; PI: D.
Riechers). Two observing runs were carried out on 2014 December 06 and 2015
February 05 under good weather conditions in the C and D array configurations,
respectively.
This resulted in 3.75 hours of cumulative six antenna-equivalent on-source
 time after discarding unusable visibility data.
The 2 mm receivers were used to cover the redshifted \bco line
and the underlying continuum emission, employing a correlator setup that provides
an effective bandwidth of 3.6 GHz (dual polarization) and a native spectral resolution of 1.95\,MHz
($\sim$\,$4.2$\,\kms).
The nearby quasars B1127$-$145 and B1124$-$186 were observed every 22 minutes
for pointing, secondary amplitude, and phase calibration, and B1055$+$018 was
observed as the bandpass calibrator for both tracks.
MWC349 and 3C279 were observed as primary flux calibrators for the C and D
array observations, respectively, yielding calibration accuracy better than 15\%.

@@

\subsection{CARMA \cco}
Observations of the \cco rotational line in RXJ1131
($\nu_{\rm rest}$\,=\,345.79599\,GHz) redshifted to $\nu_{\rm obs}$\eq209.10443\,GHz
were carried out with the \carma (CARMA;
Program ID: cf0098; PI: D. Riechers)
in the D array configuration on 2014 February 02 under poor 1.5\,mm
weather conditions and on 2014 February 17 under good 1.5\,mm
weather conditions.
This resulted in a total on-source time of 2.94 hours after flagging poor
visibility data.
The correlator setup provides a bandwidth of 3.75 GHz in
each sideband and a %native
spectral resolution of 12.5 MHz ($\sim$17.9 \kms). The
line was placed in the lower sideband with the local oscillator tuned to $\nu_{\rm LO}\sim$216 GHz. The radio quasars J1127$-$189 (first track) and 3C273
(second track) were observed
every 15 minutes for pointing, amplitude, and phase calibration. Mars was
observed as the primary absolute flux calibrator and 3C279 was observed as
the bandpass calibrator for both tracks.

@@

%--------------------------------------------------------------------------
%                                Results
%--------------------------------------------------------------------------
\section{Results} \label{sec:results}
\subsection{\bco Emission} \label{sec:CO21}
We detect \bco line emission toward the background source in the PdBI data
at $\gtrsim$\,27$\sigma$ significance, confirming the redshift at $z_{\rm CO}$ =
0.6537\,$\pm$\,0.0005. The emission is spatially and dynamically resolved
with a highly asymmetric double-horned line profile
as shown in \Fig{CO21spec}. Fitting a double Gaussian results in peak
flux densities of 75.3\pmm2.6 mJy and 24.0\pmm2.0 mJy, and a FWHM of
179\pmm9 \kms and 255\pmm28 \kms for the two components, respectively. The peaks are separated by
$\Delta v_{\rm sep}$ = 400\pmm12\,\kms. The total integrated line flux is 24.1\,$\pm$\,2.3 Jy \kms. % see 15May16/

\begin{figure}[htbp]
\centering
\includegraphics[width=0.45\textwidth]{../Figures/SpecCO21_twinx.eps}
\caption{Continuum-subtracted spectrum (histogram) of \bco emission toward RXJ1131, with a spectral resolution of
21.5\,\kms. The solid black line shows a double-Gaussian fit to the line profile.
The velocity scale is with respect to $z$\,=\,0.6537, which is approximately the line center
considering the asymmetry resulting from differential lensing.
A detailed discussion of this effect is presented in \Sec{differential}. \label{fig:CO21spec}}
\end{figure}
\vspace{.2em}
% moment 0 map, highest SNR: CASA chan=125~159 <=> GILDAS 126-160 <=> python 125-160
% - sigma = 0.305 Jy km/s/Beam
%   - note that theoretical sigma is lower = 1.5 * sqrt(160-126+1) * 21.5 ~ 0.2 Jy km/s /beam, due to higher noise in some channels with emission
We construct a zeroth order moment map, red/blue channel maps, and
first and second moment maps, as shown in \Fig{CO21mom},
using the $uv$-continuum subtracted data cube over a velocity range of
$\Delta v$ $\sim$ 750\,\kms.
The higher-order moment maps are produced using
unbinned channel maps with 3$\sigma$ clipping.
The peak flux density is 8.12\pmm0.30 Jy\,\kms\,beam\pmOne
in the intensity map.

The deconvolved source size FWHM obtained by fitting a two-dimensional Gaussian to the integrated line map in
the image plane
is 5\farcs1\pmm0\farcs72 $\times$ 3\farcs72\pmm0\farcs66,
and thus, the emission is resolved over $\sim$2.2 beams.
While the lensed emission is not strictly distributed as a two-dimensional
Gaussian;
the fit recovers the line intensity enclosed by the emitting
region, therefore we take this as an estimate on the full extent of the lensed
emission. On the other hand, if we assume that the spatial distribution of
the lensed molecular gas emission is similar to that in the optical to \nir
wavelengths, the lensed emission would be more accurately described by an
annulus, enclosing the partially complete ``Einstein ring'' and
the lensed knots (see \Fig{CO21mom}).

\begin{figure*}[!htbp]
\hspace{0.5em}
% total chan range = 126-160, which is consistent with mom0 map now (see 15May16)
% 126-144 (Red)
% ~ delta V ~410 km/s
% from [409, 0] km/s
%  144-160 (Blue)
% ~ 365 km/s
% [-324.88, 0] km/s
\includegraphics[trim=0 10 15 0, clip, width=0.452\textwidth]{../Figures/F555WCO21_mom0_single_invertedgray.eps}
\includegraphics[trim=5 -18 0 0, clip, width=0.462\textwidth]{../Figures/F555W_REDBLUE.eps}
\\
\includegraphics[trim=25 16 0 10, clip, width=0.85\textwidth]{../Figures/CO_highOmom_CLIP5sigma}
\vspace{0.1em}
\caption{Top left: overlay of the velocity-integrated \bco emission on an archival {\it HST} $V$-band (F555W)
image.
Top right: same as top left, except the contours are color-coded to represent the red- and blueshifted emission, which
are extracted by integrating over $v$\,$\in$[0, 409] \kms and $\in$[$-$325,0] \kms, respectively.
The contours in both top panels start at 3$\sigma$ and increment at steps of
$\pm$3$\sigma$, where $\sigma$\,=\,0.3 mJy beam\pmOne for the top left panel,
and
$\sigma$ = 0.4 mJy beam\pmOne (red) and 0.5 mJy beam\pmOne (blue)
for the top right panel.
The crosses denote the
location of the foreground galaxy at $z$\,=\,0.295.
Contours for the first (bottom left) and second (bottom right) moment maps of the \bco line emission
are shown in steps of
50 \kms, and 100 \kms, respectively.
The synthesis beam size is 4\farcs4 $\times$ 2\farcs0, at PA = 13$\degr$.
\label{fig:CO21mom}}
\end{figure*}

@@

\subsection{\cco Emission}
We detect \cco line emission towards RXJ1131 in the CARMA data at $\gtrsim5\sigma$ significance.
The spectrum is shown in \Fig{co32spec} and appears to be consistent with a
double-peaked profile. We estimate a line intensity of
35.7\,$\pm$\,21.9 Jy\,\kms by summing up fluxes over the FWZI
linewidth used to infer the \bco line intensity ($\sim$700 \kms).
Assuming the spatial extent of \bco and \cco is similar and therefore the emission is
magnified by the same amount, the measured line intensities
correspond to a brightness temperature ratio of
$r_{\rm 32}$\,=\,$T_{\small \cco}$$/$$T_{\small \bco}$\,=\,0.66\,$\pm$\,0.41.
Taking into account the large phase errors associated with \cco, this is consistent with
thermalized excitation within the uncertainties, as commonly observed in nuclear regions of
nearby ULIRGs and high-$z$ quasars \citep[e.g.,][]{Weiss07a, CW13}, but also
with the lower excitation seen in normal star-forming disks \citep[e.g.,][]{Dannerbauer09a, CW13}.
% see DANNERBAUER09 intro
% i.e., we cannot rule out the possibility that this guy is similar to gal. pop. of either SF modes.

\begin{figure}[!htbp]
%\centering
\includegraphics[width=0.455\textwidth]{../Figures/coOverlay.eps}
\caption{CARMA \cco line profile (solid) without continuum subtraction is
over-plotted on the continuum-subtracted PdBI \bco line profile (dashed).
The velocity scale is with respect to $z$=0.6537, which corresponds to the
dynamical center of the \bco line. The spectral resolution for \cco and \bco
is 35.8 \kms and 21.5 \kms, respectively.
 \label{fig:co32spec}}
\end{figure}

\subsection{Continuum Emission}
No 1.5\,mm continuum emission is detected at the position of \cco
down to a 3$\sigma$ limit of 2.49\,mJy beam\pmOne.
This is consistent with the spectrum shown in \Fig{co32spec}.

>>>>

\citestyle{aa}
\shorttitle{Molecular Gas Kinematics of the Strongly-lensed Quasar Host Galaxy RXJ1131$-$1231}
\shortauthors{Leung, Riechers \& Pavesi}

@@

\title{Molecular Gas Kinematics of the Strongly-lensed Quasar Host Galaxy RXS J1131$-$1231}
\author{T. K. Daisy Leung, Dominik A. Riechers, and Riccardo Pavesi}
\affil{Department of Astronomy, Space Sciences Building, Cornell University,
Ithaca, NY 14853, USA; \myemail}

@@

\begin{abstract}
We report observations of \bco and \cco line emission towards
the quadruply-lensed quasar
RXS\,J1131$-$1231 at $z$\,=\,0.654 obtained using the
\pdbi (PdBI) and the \carma (CARMA).
Our lens modeling shows that the asymmetry in the double-horned \bco line profile
is mainly a result of differential lensing, where
the magnification factor varies from $\sim$3 to $\sim$9 across
different kinematic components.
The intrinsically symmetric line profile with a conspicuous source-plane velocity
gradient suggests that
the host galaxy is an extended rotating disk, with a CO size of $R_{\rm CO}$$\sim$6\,kpc and
a dynamical mass of $M_{\rm dyn}$\ssim8\E{10}\,\Msun.
In addition, we find a secondary CO-emitting source near RXS\,J1131$-$1231 whose location is
consistent with the optically-faint companion reported in previous studies.
The lensing-corrected molecular gas masses are $M_{\rm gas}$\ssim1.4\E{10}\,\Msun
and \ssim2\E{9}\,\Msun for RXS\,J1131$-$1231 and the companion, respectively.
The gas mass fraction of $\sim$18\% inferred for RXS\,J1131$-$1231 is consistent with the trend of decreasing molecular gas fraction since $z$\ssim2 reported in recent studies.
We find lensing-corrected stellar and dust masses, an IR luminosity, and a
star formation rate of
$M_{*}$\ssim3\E{10}\,\Msun, $M_{\rm dust}$\ssim3\E{8}\,\Msun, $L_{\rm IR}$\ssim1.5\E{12}\,\Lsun,  and SFR$_{\rm FIR}$\ssim120\,\sfrU for RXS\,J1131$-$1231.
The source-plane morphologies of its gas and stellar populations
indicate that the star-formation activity may be as extended as the molecular gas reservoir.
We find a $M_{\rm BH}$$/$$M_{\rm bulge}$ ratio of $>$0.27\petm{0.11}{0.08}\% which is higher
than the 
local value, suggesting that the bulk of the black hole mass of RXSJ1131-1231 is largely in place while its stellar bulge is still assembling.
\end{abstract}

@@

%--------------------------------------------------------------------------
%                          Observations details
%--------------------------------------------------------------------------
\section{Observations} \label{sec:obs}
\subsection{PdBI \bco}
Observations of the \bco rotational line
($\nu_{\rm rest}$\,=\,$230.53800$ GHz) at the tuning frequency of 
$\nu_{\rm obs}$\eq139.256\,GHz
% redshifted to $\nu_{\rm obs}$\eq139.40739\,GHz
were carried out using IRAM \pdbi (PdBI; Program ID: S14BX; PI: D.
Riechers). Two observing runs were carried out on 2014 December 06 and 2015
February 05 under good weather conditions in the C and D array configurations,
respectively.
This resulted in 3.75 hours of cumulative six antenna-equivalent on-source
 time after discarding unusable visibility data.
The 2 mm receivers were used to cover the redshifted \bco line
and the underlying continuum emission, employing a correlator setup that provides
an effective bandwidth of 3.6 GHz (dual polarization) and a native spectral resolution of 1.95\,MHz
($\sim$\,$4.2$\,\kms).
The nearby quasars B1127$-$145 and B1124$-$186 were observed every 22 minutes
for pointing, secondary amplitude, and phase calibration, and B1055$+$018 was
observed as the bandpass calibrator for both tracks.
MWC349 and 3C279 were observed as primary flux calibrators for the C and D
array observations, respectively, yielding calibration accuracy better than 15\%.

@@

\subsection{CARMA \cco}
Observations of the \cco rotational line in RXJ1131
($\nu_{\rm rest}$\,=\,345.79599\,GHz) 
% redshifted to 
at the observe frequency of $\nu_{\rm obs}$\eq209.10443\,GHz    % i.e. where we thought the line was redshifted to 
were carried out with the \carma (CARMA;
Program ID: cf0098; PI: D. Riechers)
in the D array configuration on 2014 February 02 under poor 1.5\,mm
weather conditions and on 2014 February 17 under good 1.5\,mm
weather conditions.
This resulted in a total on-source time of 2.94 hours after flagging poor
visibility data.
The correlator setup provides a bandwidth of 3.75 GHz in
each sideband and a %native
spectral resolution of 12.5 MHz ($\sim$17.9 \kms). The
line was placed in the lower sideband with the local oscillator tuned to $\nu_{\rm LO}\sim$216 GHz. The radio quasars J1127$-$189 (first track) and 3C273
(second track) were observed
every 15 minutes for pointing, amplitude, and phase calibration. Mars was
observed as the primary absolute flux calibrator and 3C279 was observed as
the bandpass calibrator for both tracks.

@@

%--------------------------------------------------------------------------
%                                Results
%--------------------------------------------------------------------------
\section{Results} \label{sec:results}
The observed properties of \bco and \cco emission are summarized in \Tab{obsprop}.
\input{table_obsprop}

\subsection{\bco Emission} \label{sec:CO21}
We detect \bco line emission toward the background source in the PdBI data
at $\gtrsim$\,27$\sigma$ significance, enabling us to constrain its redshift at 
$z_{\rm CO}$\eq0.6541\,$\pm$\,0.0002\footnote{This redshift is derived by fitting a double-Gaussian to 
the de-lensed spectrum, which is shown in \Fig{delensed}.
% instead of the observed spectrum (\Fig{CO21spec}) to avoid biases in our 
% redshift determination of the dynamical center due to differential lensing (see \Sec{differential}).
}. The emission is spatially and kinematically resolved
with a highly asymmetric double-horned line profile
as shown in \Fig{CO21spec}. Fitting a double Gaussian results in peak
flux densities of 75.3\pmm2.6 mJy and 24.0\pmm2.0 mJy, and a FWHM of
179\pmm9 \kms and 255\pmm28 \kms for the two components, respectively. The peaks are separated by
$\Delta v_{\rm sep}$\eq400\pmm12\,\kms. The total integrated line flux is 20.3\,$\pm$\,0.6 Jy \kms. % see 15May16/

\begin{figure}[htbp]
\centering
\includegraphics[width=0.45\textwidth]{../Figures/SpecCO21_twinx.eps}
\caption{Continuum-subtracted spectrum (histogram) of \bco emission towards RXJ1131, with a spectral resolution of
21.5\,\kms. The solid black line shows a double-Gaussian fit to the line profile.
The velocity scale is with respect to $z$\,=\,0.6541, which corresponds to the line center of RXJ1131 based on
the de-lensed line profile (\Fig{delensed}).
A detailed discussion of this effect is presented in \Sec{differential}. \label{fig:CO21spec}}
\end{figure}
\vspace{.2em}
% moment 0 map, highest SNR: CASA chan=125~159 <=> GILDAS 126-160 <=> python 125-160
% - sigma = 0.305 Jy km/s/Beam
%   - note that theoretical sigma is lower = 1.5 * sqrt(160-126+1) * 21.5 ~ 0.2 Jy km/s /beam, due to higher noise in some channels with emission
We construct a zeroth order moment map, red/blue channel maps, and
first and second moment maps, as shown in \Fig{CO21mom},
using the $uv$-continuum subtracted data cube over a velocity range of
$\Delta v$ $\sim$ 750\,\kms.
The higher-order moment maps are produced using
unbinned channel maps with 3$\sigma$ clipping.
The peak flux density is 8.12\pmm0.30 Jy\,\kms\,beam\pmOne
in the intensity map.

The deconvolved source size FWHM from fitting a single two-dimensional Gaussian 
to the integrated line image yields 5\farcs1\pmm0\farcs7$\times$3\farcs7\pmm0\farcs7, 
consistent with the results obtained by $uv$-plane fitting within the uncertainties. 
% UV plane: E_GAUSS: 4.5 +/- 0.1 x 3.5 +/- 0.2
To model the complex spatial distribution of the line emission (\Fig{CO21mom}), we 
fit two independent Gaussians and find deconvolved source sizes of 
3\farcs8\pmm0\farcs4$\times$1\farcs9\pmm0\farcs4 and 3\farcs6\pmm0\farcs3$\times$1\farcs5\pmm0\farcs3.
Therefore, the emission is slightly resolved over $\sim$\,2 beams.
The lensed CO emission is unlikely to be distributed as Gaussians 
given the morphology seen in optical and \nir emission that were observed at higher resolution, 
i.e., the lensed emission of CO (without beam convolution) is more likely to have 
an annulus configuration enclosing a partially complete ``Einstein ring'' with 
structures along the arc 
and knots (see \Fig{CO21mom}). Nevertheless, the deconvolved source sizes and the
spatially offset blue wing compared to optical emission suggest that 
the CO-emitting region in RXJ1131 is more extended than its stellar (and of course quasar) emission.

\begin{figure*}[!htbp]
\hspace{0.5em}
% total chan range = 126-160, which is consistent with mom0 map now (see 15May16)
% 126-144 (Red)
% ~ delta V ~410 km/s
% from [409, 0] km/s
%  144-160 (Blue)
% ~ 365 km/s
% [-324.88, 0] km/s
\includegraphics[trim=0 10 15 0, clip, width=0.452\textwidth]{../Figures/F555WCO21_mom0_single_invertedgray.eps}
\includegraphics[trim=5 -18 0 0, clip, width=0.462\textwidth]{../Figures/F555W_REDBLUE.eps}
\\
\includegraphics[trim=25 16 0 10, clip, width=0.85\textwidth]{../Figures/CO_highOmom_CLIP5sigma}
\vspace{0.1em}
\caption{Top left: overlay of the velocity-integrated \bco emission on an archival {\it HST} $V$-band (F555W)
image.
Top right: same as top left, except the contours are color-coded to represent the red- and blueshifted emission, which
are extracted by integrating over $v$\,$\in$[$-$19, 357] \kms and $\in$[$-$395, $-$19] \kms, respectively.
The contours in both top panels start at 3$\sigma$ and increment at steps of
$\pm$3$\sigma$, where $\sigma$\,=\,0.3 mJy beam\pmOne for the top left panel,
and
$\sigma$ = 0.4 mJy beam\pmOne (red) and 0.5 mJy beam\pmOne (blue)
for the top right panel.
The crosses denote the
location of the foreground galaxy at $z$\,=\,0.295.
Contours for the first (bottom left) and second (bottom right) moment maps of the \bco line emission
are shown in steps of
50 \kms, and 100 \kms, respectively.
The synthesis beam size is 4\farcs4 $\times$ 2\farcs0, at PA = 13$\degr$.
\label{fig:CO21mom}}
\end{figure*}

@@

\subsection{\cco Emission}
We detect \cco line emission towards RXJ1131 in the CARMA data at $\gtrsim$\,5$\sigma$ significance.
The spectrum is shown in \Fig{co32spec} and appears to be consistent with a
double-peaked profile. We estimate a line intensity of
35.7\,$\pm$\,6.9\,Jy\,\kms by summing up fluxes over the FWZI
linewidth used to infer the \bco line intensity ($\sim$700 \kms).
Assuming the spatial extent of \bco and \cco is similar and therefore the emission is
magnified by the same amount, the measured line intensities
correspond to a brightness temperature ratio of
$r_{\rm 32}$\,=\,$T_{\small \cco}$$/$$T_{\small \bco}$\,=\,0.78\,$\pm$\,0.62, where this uncertainty includes 
those introduced in absolute flux calibration and is dominated by 
the large phase errors associated with the \cco observations.
This ratio is consistent with
thermalized excitation within the uncertainties, as commonly observed in nuclear regions of
nearby ULIRGs and high-$z$ quasars \citep[e.g.,][]{Weiss07a, CW13}, but also
with the lower excitation seen in normal star-forming disks \citep[e.g.,][]{Dannerbauer09a, CW13}.
% see DANNERBAUER09 intro
% i.e., we cannot rule out the possibility that this guy is similar to gal. pop. of either SF modes.

\begin{figure}[!htbp]
%\centering
\includegraphics[width=0.455\textwidth]{../Figures/coOverlay.eps}
\caption{CARMA \cco line profile (solid) without continuum subtraction is
over-plotted on the continuum-subtracted PdBI \bco line profile (dashed).
The velocity scale is with respect to $z$=0.6541, which corresponds to the
line center of \bco line emission. The spectral resolution for \cco and \bco
is 35.8 \kms and 21.5 \kms, respectively.
 \label{fig:co32spec}}
\end{figure}

\subsection{Continuum Emission} \label{sec:deblend}
No 1.4\,mm continuum emission is detected at the position of \cco
down to a 3$\sigma$ limit of 2.49\,mJy beam\pmOne.
This is consistent with the spectrum shown in \Fig{co32spec}.

We detect 2.2\,mm continuum emission at an
 integrated flux density of
1.2\pmm0.2 mJy, with a peak flux of
$S_{\nu}$\,=\,799\pmm88\,$\mu$Jy\,beam\pmOne
centered on the lensing galaxy (\Fig{cont}).
We note that the reported flux uncertainties do not include those from absolute flux calibration.
Slightly extended emission
along the lensed arc is also detected.
This suggests that we detect emission in both
the foreground galaxy and the background galaxy and that the
emission is marginally resolved along its major axis.
We subtract a point source model in the $uv$-plane to remove the unresolved part of the
emission, which we here assume to be dominated by the foreground galaxy. The peak emission 
of flux $S_{\nu}$\eq0.39\,$\pm$\,0.08\,mJy
in the residual map coincides with the lensed arc, and is consistent with
the difference between the integrated and the peak flux in the
original continuum map ($\sim$0.4 mJy). 
We therefore adopt $S_{\nu}$\eq0.39\pmm0.22 mJy as the 2\,mm continuum flux measurement for 
the background galaxy (RXJ1131). 
The quoted uncertainty is solely based on the uncertainties associated with the flux density of the 
point source model ($\delta S_{\nu}$\eq0.088\,mJy) and 
that of the integrated flux in the original data (0.2\,mJy), and does not account for that in the 
de-blending procedure, where we have assigned 100\% of the point source flux to the foreground galaxy.
We report the peak flux in the original map
($S_{\nu}$\,=\,799\pmm88\,$\mu$Jy\,beam\pmOne) for the foreground galaxy, which
is the best estimate possible at the resolution of our observations, but we acknowledge that a non-negligible contribution from the background source to the peak flux cannot be ruled out.
% The quote uncertainty on the flux density of the foreground galaxy based on the peak flux density
% assumes that the foreground galaxy is a point source, the...
